---
name: Leonardo
surname: Feitosa
position: "PhD Student"
address: "Bren School of Environmental Science, University of California, Santa Barbara"
phone: +55 98 991533001
www: "https://lmfeitos.github.io/leonardo-website/"
email: "lmfeitosa@ucsb.edu"
twitter: "@FeitosaManir"
github: "https://github.com/lmfeitos"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(scholar)
library(tibble)
library(tidyverse)
```

# Some stuff about me
## Language
* Portuguese: Native speaker
* English: Fluent speaker (TOEFL IBT: 114)
* Spanish: Good understanding

## Computer
* Microsoft office
* R programming: basic skills

## Research
* DNA extraction, amplification, and molecular data analyses
* Elasmobranch vertebrae processing, ageing, and microchemistry data analysis

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Place,
  "Biological Sciences", "2012-2017", "Universidade Federal do Maranhão", "Sao Luis, Brazil",
  "Master of Animal Biology", "2019", "Universidade Federal de Pernambuco", "Recife, Brazil",
  "PhD in Environmental Science and Management", "Ongoing (2020)", "University of California", "Santa Barbara, USA"
) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   where = Institution,
                   why = Place)
```

# Publications (Needs fixing)

```{r}
pubs <- scholar::get_publications("02Nq52RlwHEC&hl") %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = cites
  )
```

# Scholarships and Awards

```{r}
tribble(
  ~ Period, ~ Scholarship, ~ Description, ~ Duration,
  "2019", "CAPES-Fulbright PhD Scholarship Award, USA", "PhD Sponsored Student (administered by LASPAU)", "Current",
  "2017", "Graduate Scholarship Program (FACEPE), UFPE, Brazil", "Graduate Sponsored Student", "Two year position",
  "2016", "Institutional Program of Scientific Initiation Scholarships (PIBIC-CNPq), UFMA, Brazil", "Undergraduate Sponsored Student (LabAqua)", "One year position",
  "2015", "Institutional Program of Scientific Initiation Scholarships (PIBIC), UFMA, Brazil", "Undergraduate Sponsored Student (LABGEM)", "One year position",
  "2014", "Science Without Borders Program, United States of America", "Sponsored exchange student (University of Texas at Austin) - Biology Major (3.38/4.00)", "One year scholarship",
  "2012", "Tutorial Education Program (PET), UFMA, Brazil", "Undergraduate Sponsored Student", "One year scholarhip"
) %>% 
  detailed_entries(
    when = Period,
    what = Scholarship,
    with = Description,
    why = Duration
  )
```

# Professional and Volunteers Experience

```{r}
tribble(
  ~ Period, ~ Institution, ~ Function, ~ Duration,
  "2016", "Biology Department, Universidade Federal do Maranhão", "Undergraduate Teaching Assistant - Molecular Ecology course", "One semester position",
  "2013", "Biology Department, Universidade Federal do Maranhão", "Undergraduate Teaching Assistant - Systems Ecology course", "One semester position",
    "2012", "Orla Viva NGO", "Volunteered guiding visitors, and proposed and organized funding events", "Two year position"
) %>% 
  detailed_entries(
    when = Period,
    where = Institution,
    what = Function,
    why = Duration
  )
```


# Prizes

```{r}
tribble(
  ~ Year, ~ Type, ~ Desc,
  "2016", "Best Oral talk", "Carolus Maria Vooren award from the Brazilian Society for the study of Elasmobranchs",
  "2020", "Full PhD Fulbright Scholarship", "Awarded with a fully funded PhD from Fulbright Brazil and CAPES"
) %>% 
  brief_entries(
    what = Type,
    when = Year,
    with = Desc
    )
```
