---
title: "Oil Spills in California by county"
description: |
  Here is a cool little project on mapping oil spills in California
author:
  - name: Leonardo Feitosa
    url: {}
categories:
  - portfolios
date: 02-22-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(here)
library(tmap)
library(lubridate)
library(janitor)
library(sf)
```

Hello guys! 

It's been a while since I've last posted here, right?

This time I'll show you some new mapping skills I learned recently thanks to Allison Horst and Casey O'Hara!

I got data on the records of California oil spills by county in 2008 from this website https://gis.data.ca.gov/datasets/7464e3d6f4924b50ad06e5a553d71086_0/data and created a few data visualizations to show exactly where oil spills occurred in an interactive map. I also created a choropleth map based on the counts of oil spills per county so we can see where they most occurred in 2008.

Here are the plots!

```{r}
## Read in the data
### Oil spills by county
ca_oil_spills <- read_sf(here("data", "oil_spills", "Oil_Spill_Incident_Tracking_%5Bds394%5D.shp")) %>% 
  clean_names() %>% 
  rename(object_id = objectid,
         dfg_control = dfgcontrol,
         oes_number = oesnumber,
         date = dateofinci,
         inland_marine = inlandmari,
         time = timeofinci,
         location = specificlo,
         city = localecity,
         county_name = localecoun) 

  
### California counties shape file
ca_counties <- read_sf(here("data", "ca_counties", "CA_Counties_TIGER2016.shp")) %>% 
  clean_names() %>% 
  dplyr::select(name) %>% 
  rename(county_name = name)
```


```{r}
## Oil spill data wrangling
ca_oil_spills_tidy <- ca_oil_spills %>%
  mutate(date = as.Date(date)) %>% 
  mutate(date = ymd(date)) %>% 
  mutate(year = year(date)) %>% 
  dplyr::select(date, year, longitude, latitude, city, county_name, inland_marine)
```

```{r, include = FALSE}
## set crs for both datasets
ca_counties %>% st_crs()
ca_oil_spills_tidy %>% st_crs()

```


```{r, include = FALSE}
ggplot() +
  geom_sf(data = ca_counties,
          color = "gray18",
          size = 0.1) +
  geom_sf(data = ca_oil_spills_tidy,
          color = "black",
          size = 0.5) +
  theme_bw()
```

## Interactive map of California oil spills in 2008

```{r}
tmap_mode("view")

tm_shape(ca_counties) +
  tm_fill("county_name", palette = "Purples", title = "County") +
  tm_shape(ca_oil_spills_tidy) +
  tm_dots(size = 0.03, col = "darkorange2", border.col = "black") +
  tm_view(view.legend.position = "left")
```




## Data visualization of inland oil spills records in California in 2008

```{r}
## Counts of California oil spills by county
ca_oil_spills_join <- ca_counties %>% 
  st_join(ca_oil_spills_tidy)

oil_spills_count <- ca_oil_spills_join %>% 
  filter(inland_marine %in% c("Inland")) %>% 
  count(county_name.x, inland_marine) %>%
  mutate(n = as.numeric(n))


ggplot(data = oil_spills_count) +
  geom_sf(aes(fill = n),
          color = "black",
          size = 0.5) +
  scale_fill_viridis_c() +
  labs(title = "Inland oil spill records by county in California for 2008",
       fill = "Number of oil spill records") +
  theme_bw() +
  theme(axis.text = element_text(size = 10, face = "bold", color = "black"),
        panel.grid = element_blank())
```

